### 2014-10-15 Docs/runtime_parameters/runtime_parameters.tex
removed do_alltoallv parameter becuase BoxLib already stopped doing that 3 years ago
sync with latest

\rowcolor{tableShade}
\verb=  barrier_timers  = &   Call a parallel\_barrier before each of the simple timers we have coded in advance.f90.  Might cause a very slight overall performance hit.  &  .false. \\
\verb=  do_alltoallv  = &   use the MPI alltoallv call  &  .false. \\
\rowcolor{tableShade}
\verb=  job_name  = &   job name printed in output  &  "" \\
\verb=  the_knapsack_verbosity  = &   Verbosity of the knapscak processor-to-grid algorithm.  &  .false. \\
\rowcolor{tableShade}
\verb=  verbose  = &   General verbosity  &  0 \\

@@

@@

@@

\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  25 \\

>>>>

\rowcolor{tableShade}
\verb=  barrier_timers  = &   Call a parallel\_barrier before each of the simple timers we have coded in advance.f90.  Might cause a very slight overall performance hit.  &  .false. \\
\verb=  job_name  = &   job name printed in output  &  "" \\
\rowcolor{tableShade}
\verb=  the_knapsack_verbosity  = &   Verbosity of the knapscak processor-to-grid algorithm.  &  .false. \\
\verb=  verbose  = &   General verbosity  &  0 \\

@@

\verb=  ignore_fine_in_layout_mapping  = &   Our traditional way of distributing boxes among MPI ranks has a flaw.  In some cases, it unnecessarily moves grids among processors in regridding.  Even if the grids do not changes at all, the boxes may end up on different processors after regridding, and the box distribution becomes more and more fragmented over time (i.e. neighboring boxes become far away from each other in MPI ranks).  Setting {\tt ignore\_fine\_in\_layout\_mapping} to true will avoid the flaw.  &  .true. \\

@@

\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  50 \\

@@
